Fair, Stable Exchange Networks through Quenched Merchant Location and Idiosyncratic Trading Costs

### 2019-06-22 writing/Paper/main.tex
took care of figure caption

\documentclass[11pt]{article}
\usepackage[a4paper,margin=2.8cm]{geometry}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{cancel}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage[dvipsnames,usenames]{color}
\usepackage[colorlinks=true,linkcolor=NavyBlue,citecolor=NavyBlue,urlcolor=NavyBlue]{hyperref} % for hyperlinks

@@

\begin{figure}
  \includegraphics[width=\linewidth]{5x2plot.png}
  \caption{Shown above are five instances of the model running for different
  $\gamma$ and costs. In the first two rows, $\gamma=0$, with the one
  difference being that in Row 1, both Firm 1 and Firm 2 have the same cost,
  and in Row 2, Firm 1 has a 1\% lower cost than Firm 2. In Row 1, the firms
  sell the same amount of product and make the same amount of profit. But in
  Row 2, Firm 1 sells 33\% more quantity and makes 53\% more profit.
  In the rest of the plots, $\gamma = .6$. In Row 3 we can see a mirror of Row
  1, where both firms, faced with the same costs, produce the same quantity,
  and make the same profit. But in row 4, where we give Firm 1
  the same advantage we game them in the row 2, they sell the same amount, and
  only make 12\% more profit than Firm 2. To increase their market share,
  Firm 1 needs to reduce their costs to 80\% of Firm 2, as shown in row 5.
  Our idiosyncratic tax thus acts as a speed bump, preventing companies with
  slight advantages from acquiring overwhelming market dominance, while still
  ensuring that minor innovations are profitable, and that large innovations do
  cause market dominance.}
  \label{fig:fig3x2SingleTimestep}
\end{figure}

>>>>

\documentclass[11pt]{article}
\usepackage[a4paper,margin=2.8cm]{geometry}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{cancel}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage[dvipsnames,usenames]{color}
\usepackage[colorlinks=true,linkcolor=NavyBlue,citecolor=NavyBlue,urlcolor=NavyBlue]{hyperref} % for hyperlinks 
\usepackage{floatpag} % remove page number for figure that covers entire page

@@

\begin{figure}[[p!htb] % p stands for 'entire page', '!htb' is to insert as close to code as possible
	\floatpagestyle{empty} % remove page number
	\centering
	\vspace{-2cm} % shift upwards to get more space for caption
  \includegraphics[width=\linewidth]{5x2plot.png}
  \caption{\small{Shown above are five instances of the model running for different
  $\gamma$ and costs. In the first two rows, $\gamma=0$, with the one
  difference being that in Row 1, both Firm 1 and Firm 2 have the same cost,
  and in Row 2, Firm 1 has a 1\% lower cost than Firm 2. In Row 1, the firms
  sell the same amount of product and make the same amount of profit. But in
  Row 2, Firm 1 sells 33\% more quantity and makes 53\% more profit.
  In the rest of the plots, $\gamma = .6$. In Row 3 we can see a mirror of Row
  1, where both firms, faced with the same costs, produce the same quantity,
  and make the same profit. But in row 4, where we give Firm 1
  the same advantage we game them in the row 2, they sell the same amount, and
  only make 12\% more profit than Firm 2. To increase their market share,
  Firm 1 needs to reduce their costs to 80\% of Firm 2, as shown in row 5.
  Our idiosyncratic tax thus acts as a speed bump, preventing companies with
  slight advantages from acquiring overwhelming market dominance, while still
  ensuring that minor innovations are profitable, and that large innovations do
  cause market dominance.}}
  \label{fig:fig3x2SingleTimestep}
\end{figure}
